Modelling the emergence of whisker barrels

### 2020-06-29 paper/briefpaper/brief.tex
Adds an initial Fig 5 (but I'm not happy with it yet) and does some word wrapping of brief.text

\documentclass[9pt,lineno,draft]{elife}

@@

To further investigate the interplay of genetic and intrinsic mechanisms we
simulated a seminal barrel duplication experiment
\citep{shimogori_fibroblast_2005}, first by solving on a cortical domain
comprising two separate, identically shaped cortical boundaries. In this case
one distinct cortical field per thalamic projection emerged, within one of the
two boundaries only, i.e., no duplication. However, merging the two fields to
create an extended mirror-symmetric boundary shape, with an anterior-posterior
guidance field reflected at the join, gave rise to two mirror-symmetrical
barrel fields comprising 2N barrels, i.e., two cortical fields for each
thalamic projection (Fig.\,\ref{fig:fgf8}). Together these results suggest that by the
misexpression of Fgf8, \cite{shimogori_fibroblast_2005}
effectively created one large barrel field rather than two distinct cortical
fields. \cmnt{Add something about the slightly off-vertical arrangement of the
  fields.}

>>>>

\documentclass[9pt,lineno]{elife}

@@

To further investigate the interplay of genetic and intrinsic mechanisms we
simulated a seminal barrel duplication experiment
\citep{shimogori_fibroblast_2005}, first by solving on a cortical domain
comprising two separate, identically shaped cortical boundaries. In this case
\cmnt{NOTE: The following only holds for the divisive normalization system -
  in the comp2 system, there's no `coupling' at all between the two regions,
  so the mirrored region arranges itself as expected with the one reversed
  guidance field.} one distinct cortical field per thalamic projection emerged, within one of the
two boundaries only, i.e., no duplication. However, merging the two fields to
create an extended mirror-symmetric boundary shape, with an anterior-posterior
guidance field reflected at the join, gave rise to two mirror-symmetrical
barrel fields comprising 2N barrels, i.e., two cortical fields for each
thalamic projection (Fig.\,\ref{fig:fgf8}). Together these results suggest that by the
misexpression of Fgf8, \cite{shimogori_fibroblast_2005}
effectively created one large barrel field rather than two distinct cortical
fields. \cmnt{Add something about the slightly off-vertical arrangement of the
  fields.}

\begin{center}
  \includegraphics[width=\linewidth]{./Fig5.png}
  \captionof{figure}{\cmnt{Simulating whisker trimming by reduction of
      $\epsilon$ for the thalamocortical projection for barrel C3, for which
      $i=13$. All other model parameters match those in
      Fig.\,\ref{fig:main}C. \textbf{A} Graph of individual barrel measures
      plotted vs.~the multiplier applied to $\epsilon_{13}$. \textbf{B} The
      pattern for $\epsilon_{m}=0.64$.}}
  \label{fig:whiskertrim}
\end{center}
